\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements} % Add to table of contents

\justifying

I would like to express my heartfelt gratitude to my project guide, 
\textbf{Dr. Suryakant V Gangashetty}, for his invaluable guidance, continuous support, 
and encouragement throughout the course of this project. His expertise in artificial intelligence 
and deep learning, coupled with his patient mentorship, played a pivotal role in shaping 
the direction and execution of this research.

From the inception of the idea to the final implementation and evaluation, 
his insights and constructive feedback helped me navigate technical challenges 
and refine the project to its fullest potential. His mentorship not only enriched my learning experience 
but also inspired me to push the boundaries of my knowledge. His advice on evaluating 
different models helped achieve the optimum performance in the Hybrid move_car model.

I am sincerely thankful for the opportunity to work under his mentorship, 
and I truly appreciate his commitment, time, and support during every stage of this M.Tech journey.

\vspace{0.5cm}

The authors also extend their sincere gratitude to the Indian Institute of Technology Jammu 
for providing essential computational resources, which were critical to the successful execution of this research. 
Furthermore, profound appreciation is conveyed to the open-source community for their foundational contributions, 
which have significantly advanced the field of autonomous driving and provided indispensable tools 
and knowledge integral to this project.
